### 2017-03-28 paper/modes.tex
Sec 2: reorganized + commented unnecessary details + removed some TODOs

The list below shortly describes the choices to control parallelism
within a JVM.

@@

Several build systems support the execution of test classes in forked
processes running a Java virtual machine (JVM). Each spawned process
runs a test class at time. In addition, the builder can reuse these
processes to execute the next test classes in the queue according to
the developer's preference. For instance, one might want the builder
to spawn a new process for each test class to ensure maximum
isolation.  To exploit parallelism at this level, the number of forked
processes must be proportional to the number of available CPUs,
otherwise, the high frequency of context-switching and concurrency
(\ie, processes competing for a CPU time-slice) may affect the
performance.  For instance, if the underlying machine has four CPUs
available, the builder could be configured to spawn one process on
each core in contrast to several processes competing for a single
core.

Builder-level parallelism can also complement some testing framework
parallelism levels. For instance, \Fix{elaborate...}.  However, some
settings may not take effect since only one test class can run in a
forked process at time. For instance, \Fix{elaborate...}. To the best
of our knowledge, we are unaware of any build system capable of
running multiple classes at time within a forked process.

In this paper, we use the prefix ``\Fork{}'' to indicate that a given
testing configuration has the feature of spawning JVMs to run test
classes enabled. The list below shortly describes the choices to
control parallelism:

\begin{itemize}
\item
    \textbf{Forked classes; sequential methods (\ForkSeq).}~\Fix{todo}
\item
    \textbf{Forked classes; parallel methods (\ForkParMeth).}~\Fix{todo}
\end{itemize}

\subsubsection*{Illustration}~\Fix{elaborate}

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <reuseFork>true</true>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Maven with a \ForkParMeth{}
    configuration. Maven forks one JVM per core (\CodeIn{forkCount}
    parameter) and \Jbc{check this $\rightarrow$} uses five threads
    (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
    parameter) within each test class.}

>>>>

The list below shortly describes the choices to control parallelism
within a Java virtual machine (JVM).

@@

The list below shortly describes the choices to control parallelism
through build systems:

\begin{itemize}
\item
    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
        configuration corresponds to the parallel execution of test
        classes on different JVMs and test methods run sequentially
        within each JVM.
\item
    \textbf{Forked classes; parallel methods (\ForkParMeth).}~This
        configuration corresponds to the parallel execution of test
        classes on different JVMs and test methods run on multiple
        threads within each JVM.
\end{itemize}

Several build systems support the execution of test classes in forked
processes running a JVM. In the \ForkSeq{} configuration, each spawned
process runs a different test class at time and the builder merges the
results from each execution. In the \ForkParMeth{} configuration, the
build system forwards settings to the underlying testing framework to
enable parallel execution within each process in addition to running
test classes on different processes.  However, some configurations
(\eg, \ParClassSeqMeth) may not take effect since only one test class
can run in a forked process at time.  To the best of our knowledge, we
are unaware of any build system capable of running multiple classes at
time within a forked process.  \Comment{In addition, the builder can
reuse these processes to execute the next test classes in the queue
according to the developer's preference. For instance, one might want
the builder to spawn a new process for each test class to ensure
maximum isolation. Notice that to exploit parallelism at build system
level, the number of forked processes must be proportional to the
number of available CPUs, otherwise, the high frequency of
context-switching and processes competing for a CPU may degrade the
execution performance  \Jbc{$\leftarrow$ I'm not sure if we should
keep this. We can remove it if necessary}.}

%% In this paper, we use the prefix ``\Fork{}'' to indicate that a given
%% testing configuration has the feature of spawning JVMs to run test
%% classes enabled.

\subsubsection*{Illustration}~\Fix{elaborate the following example to
conclude this section}

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Maven with a \ForkParMeth{}
    configuration. Maven forks one JVM per core (\CodeIn{forkCount}
    parameter) and \Jbc{check this $\rightarrow$} uses five threads
    (\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
    parameter) within each JVM.}
